---
title: "Analysis notebook for  Association between in-ICU red blood pack transfusion and long-term outcome in the ICU survivors"
subtitle: "Illustration on a small subsample"
author: " Imke Mayer, Paul Roussel, Antoine Kimmoun, Thomas Merkling, Kevin Duarte, Julie Josse"
output:
  html_document:
    code_folding: hide
    theme: journal
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document: null
editor_options:
  chunk_output_type: inline
always_allow_html: yes
---

```{=html}
<style type="text/css">

h1.title {
  font-size: 38px;
  text-align: center;
}

h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  text-align: center;
}

h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  text-align: center;
}
</style>
```

# Description

This notebook is provided as a complementary to the article 
* Association between in-ICU red blood pack transfusion and long-term outcome in the ICU survivors*.
It contains the R code to run all analyses that are presented in the article.
Since the FROG dataset is not a publicly available, we provide a random subsample
of size n=200 and only the relevant variables for the causal analyses to allow the 
reader to run all lines of code related to the survival analyses and causal inferences
presented in the article.
The calculated results from this random subsample of size n=200 do not allow to
conclude on the medical problem of interest, they are merely used as illustrations
for the provided code and data structure.

The different methods and models are detailed in the paper and the supplementary material.
We therefore do not recall them here.


```{r, echo=FALSE}
knitr::opts_chunk$set(error = FALSE, warning=FALSE)
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# markdown options depending on the output (html with R code and Word without)
output <- knitr::opts_knit$get("rmarkdown.pandoc.to")
if (output=="html") knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = TRUE, comment = "", fig.align = "center", fig.width= 9, fig.height=9)
if (output=="docx") knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE, comment = "", fig.align = "center", fig.width= 9, fig.height=9)
if (output=="pdf") knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE, comment = "", fig.align = "center", fig.width= 9, fig.height=9)

options(max.print = .Machine$integer.max)
```

# Packages

```{r,include=FALSE}
library(readr)
library(FactoMineR)
library(missMDA)
library(WeightIt)
library(cowplot)
library(simsurv)
library(flexsurv)
library(MASS)
library(survMisc)
library(matrixStats)
library(RISCA)
library(readxl)
library(riskRegression)
library(reshape2)
library(rms)
library(devtools)
library(boot)
library(readxl)
library(Epi)
library(flextable)
library(moments)
library(stringr)
library(lubridate)
library(DiagrammeR)
library(rstatix)
library(survminer)
library(tidyr)
library(missMDA)
library(mice)
library(factoextra)
library(stdReg)
library(maditr)
library(outliers)
library(VIM)
library(survival)
library(ggplot2)
library(dplyr)
library(survminer)
library(MatchThem)
library(pbapply)
library(ggfortify)
library(knitr)
require(miceadds)
library(forcats)
library(glmnet)    
library(grf)       
library(sandwich)  
library(tableone)  
library(cobalt)    
library(ranger)
library(Matching)  
library(survey)  
library(psych)
library(patchwork)
library(gtsummary)
library(PropCIs)
library(stringr)
```

# Load

```{r,include=FALSE,cache=TRUE}
set.seed(2600)
load(file="DATA_PUBLIC/clean_data_FROG_TRANSFUSION_subsample200")


source("FUNCTIONS_PUBLIC/utils_surv.R")
source("FUNCTIONS_PUBLIC/function_table1.R")
source("FUNCTIONS_PUBLIC/function_FROG_TRANSFU.R")
source("FUNCTIONS_PUBLIC/RCS_plot_LogisticCox.R")
source("FUNCTIONS_PUBLIC/causal_survival_function.R")
source("FUNCTIONS_PUBLIC/customize_labels.R")
```

# Systematic preprocessing

```{r,cache=FALSE,include=T}
# for table 1
DATAtab1<-DATA

# Choose baseline confounding from DAG
numerical_baseline_confounding = c(
  'age',
  'ia_igs_2',
  'csabad_sofa', 
  'csabad_hb',
  'csabad_systolic_blood_pressure',
  'csabad_diastolic_blood_pressure',
  'csabad_heart_rate',
  'csabad_eGFR',
  'csabad_creat_umol_L',
  'csabad_lactate',
  'csabad_rate_of_prothrombin'
)

str(DATA[numerical_baseline_confounding])


categorical_baseline_confounding <- c(
  'initial_admission_unit', 
  'diagnostic_codeJ',
  'ia_mac_cab',
  'gender',
  "ct_antiplatelets",
  "ct_none_of_the_above",
  "cm_chronic_heart_failure",
  "cm_hypertension",
  "cm_coronary_artery_disease",
  "cm_none_of_the_above",
  "ncm_chronic_renal_disease",
  "ncm_active_recent_malignant_tumors", 
  "ncm_anemia",
  "ncm_none_of_the_above",
  "mfi_rbc_transfusion" ,
  "mfi_renal_replacement_therapy", 
  "mfi_coronary_revascularisation",
  'seuil_transfu_10',
  "mfi_heparin",
  "mfi_antiplatelets"
)


str(DATA[categorical_baseline_confounding])

confounder_names <- c(numerical_baseline_confounding,categorical_baseline_confounding)
only_outcome_pred_names <- c(
  'CRP_T1',
  'GAL_T1',
  'PCT_T1',
  'hsTnI_T1',
  'LFABP_T1',
  'CYSC_T1',
  'NGAL_T1',
  'IL6_T1',
  'PROBNP_T1'
)


str(DATA[only_outcome_pred_names])

discharge_names<-c("HB_minT",
                   "hapto_T2",
                   "GAL_T2",
                   "PROBNP_T2",
                   "NGAL_T2",
                   "NGAL_U_T2",
                   "CYSC_U_T2",
                   "LFABP_U_T2",
                   "PENK_T2",
                   "IL6_T2",
                   "hsTnI_T2",
                   "hapto_IL6_log10",
                   "sid_eGFR",
                   "sid_eGFR_cut",
                   "sid_creat_umol_L",
                   "dose_rbc")

str(DATA[,discharge_names])



# Variable names:

X_censoring <-  X_outcome <- c(numerical_baseline_confounding,
                               categorical_baseline_confounding,only_outcome_pred_names)

X_treatment <- X_confounding <- c(numerical_baseline_confounding,
                                  categorical_baseline_confounding)



DATA_without_discharge <- within(DATA,rm("HB_minT",
                                         "hapto_T2",
                                         "GAL_T2",
                                         "PROBNP_T2",
                                         "NGAL_T2",
                                         "NGAL_U_T2",
                                         "CYSC_U_T2",
                                         "LFABP_U_T2",
                                         "PENK_T2",
                                         "IL6_T2",
                                         "hsTnI_T2",
                                         "hapto_IL6_log10",
                                         "sid_eGFR",
                                         "sid_eGFR_cut",
                                         "sid_creat_umol_L",
                                         "dose_rbc"))

DATA_with_discharge <- DATA

tau <- 365
```

# Preprocessing imputation and boostrap

## Imputation

```{r, eval=FALSE, include=T}
#without discharge
imp <- mice(DATA, maxit=0)
predM = imp$predictorMatrix
meth = imp$method
meth["ncm_anemia"] <- "pmm"

imp <- mice(DATA_without_discharge, maxit=0)
predM = imp$predictorMatrix
meth = imp$method
meth["ncm_anemia"] <- "pmm"

imputation_number <- 15 
mice_without <- mice(DATA_without_discharge,
                     maxit = 10,
                     predictorMatrix=predM, 
                     method = meth,
                     m = imputation_number,
                     printFlag = F)

mi.res_without <- mice_without
save(mice_without, file = "DATA_PUBLIC/mice_without_discharge_impute_15_maxit10_final.Rdata")

#with discharge
DATAtab1$sid_creat_umol_L
imp <- mice(DATA_with_discharge, maxit=0)
predM = imp$predictorMatrix
meth = imp$method
meth["ncm_anemia"] <- "pmm"

imputation_number <- 15 

mice_with <- mice(DATA_with_discharge,
                  maxit = 10,
                  m = imputation_number,
                  method = meth,
                  printFlag = F)

mi.res_with <- mice_with
save(mice_with, file ="DATA_PUBLIC/mice_with_discharge_impute_15_maxit10_final.Rdata" )
```


```{r, eval=T, include=FALSE}
imp<-load("DATA_PUBLIC/mice_with_discharge_impute_15_maxit10_final.Rdata")
mi.res_with<-mice_with


# distribution of the imputed values in red as compared to the real values in blue
stripplot(mi.res_with, GAL_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, PENK_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, NGAL_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, hsTnI_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, NGAL_U_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, PROBNP_T2 ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, sid_eGFR ~ .imp, pch=20, cex=2)
stripplot(mi.res_with, sid_creat_umol_L ~ .imp, pch=20, cex=2)
```


### Bootstrap without imputation

```{r}
bootstrap_number <- 100
```

```{r, include=FALSE,eval=FALSE}
l_bootstrap_100 <- list()
for (i in c(1:bootstrap_number)){
    DATA_boot <- sample_n(DATA_without_discharge, nrow(DATA_without_discharge), replace = TRUE)
    l_bootstrap_100[[i]] <- DATA_boot
}
```

### Imputation after bootstrap:

```{r, include=T,eval=FALSE}
imp <- mice(DATA_without_discharge, maxit=0)
predM = imp$predictorMatrix
meth = imp$method
meth["ncm_anemia"] <- "pmm"
meth["mfi_antiplatelets"] <- "pmm"
meth["cm_none_of_the_above"] <- "pmm"

imputation_number <- 10

list_no_error = c()
list_mice_100bootmi <- list()
for (i in 1:bootstrap_number){
  tryCatch({
  DATA_boot <- l_bootstrap_100[[i]]
  mice_without <- mice(DATA_boot,
                     maxit = 10,
                     m = imputation_number,
                     method = meth,
                     printFlag = F)
  list_mice_100bootmi[[i]] <- mice_without
  list_no_error <- c(list_no_error,i)
  }, error = function(msg){list_no_error <- c(list_no_error,FALSE)})
    print(i)
}



list_mice_100bootmi <- list_mice_100bootmi[list_no_error][1:100]
save(list_mice_100bootmi, file="DATA_PUBLIC/list_mice_100bootmi_final")

l_bootstrap_100 <- l_bootstrap_100[list_no_error][1:100]
save(l_bootstrap_100, file="DATA_PUBLIC/DATA_bootstrap_100_final")
```



### Load lists of bootstrap samples and imputations

```{r, include=FALSE,eval=T}
load("DATA_PUBLIC/DATA_bootstrap_100_final")
load("DATA_PUBLIC/list_mice_100bootmi_final")
load("DATA_PUBLIC/mice_with_discharge_impute_15_maxit10_final.Rdata")
load("DATA_PUBLIC/mice_without_discharge_impute_15_maxit10_final.Rdata")

mi.res_without <- mice_without
mi.res_with <- mice_with
```



# Estimation

## Average treatment effect

### MICE with logistic + Cox regression


```{r, include=T, eval=FALSE}
all_survival_estimator_cox <- pbsapply(list_mice_100bootmi,
                                       function(mice_without) {
    try(list_DATA_input <- complete(mice_without,"all"))
    resapply <- sapply(list_DATA_input,
                       function(DATA) try(unlist(estimate_ATE_all(DATA, tau, outcome_type="RMST", 
                                                            methods=c("Kaplan_meier","IPTW Kaplan_meier","AIPTW-AIPCW"),
                                                            outcome_name=X_outcome, censoring_name=X_censoring, treatment_name=X_confounding, 
                                                            outcome_learner="Slearner", censoring_learner="Slearner",
                                                            type_of_censoring_model ="cox", type_of_outcome_model="cox",
                                                            type_of_treatment_model="reglog", 
                                                            trimming_value_lower=0, trimming_value_upper=0, stabilized_IPTW=FALSE))))
    if (is.null(dim(resapply))){
      return(rep(NA,3))
    }
    return(rowMeans(resapply,na.rm = T))
  })

all_survival_estimator_cox <-as.data.frame(t(all_survival_estimator_cox))
all_survival_estimator_cox
summary(all_survival_estimator_cox)

write.csv(all_survival_estimator_cox,"DATA_PUBLIC/all_survival_estimators_cox_bootmi_365_final.csv", row.names = FALSE)
```

```{r, include=FALSE, eval=T}
all_survival_estimator_cox <- read.csv("DATA_PUBLIC/all_survival_estimators_cox_bootmi_365_final.csv")

label <- colnames(all_survival_estimator_cox)
mean  <- unlist(lapply(all_survival_estimator_cox, mean, na.rm = TRUE))
median  <- unlist(lapply(all_survival_estimator_cox, median, na.rm = TRUE))
lower <- unlist(lapply(all_survival_estimator_cox, quantile, probs=c(0.025), na.rm=TRUE))
upper <- unlist(lapply(all_survival_estimator_cox, quantile, probs=c(0.975), na.rm=TRUE))

df_cox <- data.frame(label, mean, lower, upper)
df_cox
```


### Forest + MIA


```{r, include=FALSE,eval=FALSE}
all_survival_estimator_forest <- pbsapply(l_bootstrap_100,function(DATA) { return(unlist(estimate_ATE_all(DATA,365,outcome_type="RMST",methods=c("Kaplan_meier","IPTW Kaplan_meier"),outcome_name=X_outcome,censoring_name=X_censoring,treatment_name=X_confounding,outcome_learner="Tlearner",type_of_censoring_model ="forest",type_of_outcome_model="forest",censoring_learner="Tlearner",type_of_treatment_model="forest",trimming_value_lower=0,trimming_value_upper=0,stabilized_IPTW = FALSE)))

  })


all_survival_estimator_forest <-as.data.frame(t(all_survival_estimator_forest))
all_survival_estimator_forest
summary(all_survival_estimator_forest)



csf_wrapper <- function(DATA, tau, X_outcome_name, X_treatment_name){
DATA_grf <- DATA
DATA_grf$A <- as.numeric(DATA$A)-1
DATA_grf$status[DATA_grf$T_obs>=tau] <- 1
DATA_grf$T_obs[DATA_grf$T_obs>=tau] <- tau  

DATA_grf_treatment <- DATA_grf
categorical_name <- names(which(sapply(subset(DATA_grf, select = c(X_treatment_name)), class) == "factor"))
if (length(categorical_name) >0){
      numerical_name <- setdiff(X_treatment_name,categorical_name)
      na.action <- options()$na.action
      options(na.action='na.pass')
      X_one_hot <- model.matrix(~ 0 + ., DATA_grf[categorical_name], na.action = "na.pass")
      categorical_name_one_hot <- names(as.data.frame(X_one_hot))
      replace_string <- function(string) {return(stringr::str_replace_all(string, ' ', '_'))}
      categorical_name_one_hot <- sapply(categorical_name_one_hot,replace_string)
      DATA_grf_treatment[categorical_name_one_hot] <- X_one_hot
      X_treatment_name <- union(categorical_name_one_hot,numerical_name)
      options(na.action = na.action)
}
forest.W <- regression_forest(as.matrix(DATA_grf_treatment[, X_treatment_name]), DATA_grf_treatment$A, tune.parameters = "all")
W.hat <- predict(forest.W)$predictions
  
categorical_name <- names(which(sapply(subset(DATA_grf, select = c(X_outcome_name)), class) == "factor"))
if (length(categorical_name) >0){
      numerical_name <- setdiff(X_outcome_name,categorical_name)
      na.action <- options()$na.action
      options(na.action='na.pass')
      X_one_hot <- model.matrix(~ 0 + ., DATA_grf[categorical_name], na.action = "na.pass")
      categorical_name_one_hot <- names(as.data.frame(X_one_hot))
      replace_string <- function(string) {return(stringr::str_replace_all(string, ' ', '_'))}
      categorical_name_one_hot <- sapply(categorical_name_one_hot,replace_string)
      DATA_grf[categorical_name_one_hot] <- X_one_hot
      X_outcome_name_grf <- union(categorical_name_one_hot,numerical_name)
      options(na.action = na.action)
}
cs.forest <- causal_survival_forest(X=as.matrix(DATA_grf[,X_outcome_name_grf]),
                                    Y=DATA_grf$T_obs, W=DATA_grf$A,
                                    
                                    D=DATA_grf$status,
                                    W.hat=W.hat)


# Compute a doubly robust estimate of the average treatment effect.
return(average_treatment_effect(cs.forest))
}


all_survival_estimator_csf <- pbsapply(l_bootstrap_100, function(DATA) { return(unlist(csf_wrapper(DATA,365,X_outcome,X_treatment)))
  })

all_survival_estimator_csf <- as.data.frame(t(all_survival_estimator_csf))
colnames(all_survival_estimator_csf) <- "AIPTW-AIPCW"
all_survival_estimator_csf[,1]

all_survival_estimator_forest <- cbind(all_survival_estimator_forest, "AIPTW-AIPCW"=all_survival_estimator_csf[,1])

write.csv(all_survival_estimator_forest,"DATA_PUBLIC/all_survival_estimators_forest_100boot_365_final.csv", row.names = FALSE)
```

```{r, include=FALSE, eval=T}
all_survival_estimator_forest <- read.csv("DATA_PUBLIC/all_survival_estimators_forest_100boot_365_final.csv")

label <- colnames(all_survival_estimator_forest)
mean  <- unlist(lapply(all_survival_estimator_forest, mean, na.rm = TRUE))
median  <- unlist(lapply(all_survival_estimator_forest, median, na.rm = TRUE))
lower <- unlist(lapply(all_survival_estimator_forest, quantile, probs=c(0.025), na.rm=TRUE))
upper <- unlist(lapply(all_survival_estimator_forest, quantile, probs=c(0.975), na.rm=TRUE))

df_forest <- data.frame(label, mean, lower, upper)
df_forest
```


## Propensity scores

### Parametric propensity score

```{r,include=T,eval=FALSE}
# We compute the mean of the propensity score on each imputed data set of the multiple imputation

results_e_hat <- matrix(NA, nrow = nrow(DATA), ncol = imputation_number)
for (j in c(1:imputation_number)){
  DATA_imp <- complete(mi.res_without, j)
  outcome <- 'A'
  f <- as.formula(paste(outcome, paste(c(X_confounding), collapse = " + "), sep = " ~ "))
  fitA <- glm(f,data = DATA_imp,family = binomial(link="logit"))
  e_hat <- predict(fitA,newdata=DATA_imp,type="response")
  results_e_hat[,j] <- e_hat
  print(j)
}
e_hat_mean <- rowMeans(results_e_hat)

# We save the mean of the propensity scores
save(e_hat_mean, file="DATA_PUBLIC/e_hat_mean_final")
```

### Non-parametric propensity score

```{r,include=T,eval=FALSE}
# We compute the mean of the propensity score on each imputed data set of the multiple imputation
results_e_hat_forest <- matrix(NA, nrow = nrow(mi.res_without$data), ncol = imputation_number)
for (j in c(1:imputation_number)){
  DATA_imp <- complete(mi.res_without, j)
  DATA_imp$A <- as.numeric(DATA_imp$A) - 1
  DATA_imp <- as.data.frame(DATA_imp)
  categorical_name <- names(which(sapply(subset(DATA_imp, select = c(X_confounding)), class) == "factor"))
  numerical_name <- setdiff(X_confounding,categorical_name)
  options(na.action='na.pass')
  X_one_hot <- model.matrix(~ 0 + ., subset(DATA_imp, select = c(categorical_name)), na.action = "na.pass")
  categorical_name_one_hot <- names(as.data.frame(X_one_hot))
  replace_string <- function(string) {return(str_replace_all(string, ' ', '_'))}
  categorical_name_one_hot <- sapply(categorical_name_one_hot,replace_string)
  DATA_imp[categorical_name_one_hot] <- X_one_hot

  X_confounding_one_hot <- union(categorical_name_one_hot,numerical_name)

  Xipw <- as.matrix(DATA_imp[X_confounding_one_hot])
  Wipw <- as.matrix(DATA_imp$A)
  forest.W <- regression_forest(Xipw, Wipw, tune.parameters = "all")
  e_hat <- predict(forest.W)$predictions
  
  results_e_hat_forest[,j] <- e_hat
  print(j)
}

e_hat_mean_forest <- rowMeans(results_e_hat_forest)

# We save the mean of the propensity scores
save(e_hat_mean_forest, file="DATA_PUBLIC/e_hat_mean_forest_final")
```



### Love plot

```{r,include=FALSE,eval=T}
outcome <- 'A'
f <- as.formula(paste(outcome, paste(c(X_confounding), collapse = " + "), sep = " ~ "))


loveplot.out <- weightthem(f, datasets = mi.res_without, approach = "within", method = "ps")

summary(loveplot.out)
#dans weightthem => correspond bien à IPTW car pas de nearest, tous les patients sont dedans



bal.tab(loveplot.out,
        abs = TRUE,
        #weights = "weights",
        thresholds = c(m = .1, v = 2))


var.names<-c(age="age",
             csabad_sofa="SOFA at I",
             csabad_systolic_blood_pressure="systolic blood pressure at I",
             csabad_heart_rate="heart rate at I ",
             csabad_creat_umol_L="creatinin at I",
             csabad_rate_of_prothrombin="PT rate at I",
             diagnostic_code="diagnostic",
             gender="gender",
             cm_hypertension="hypertension",
             csabad_diastolic_blood_pressure="diastolic blood pressure at I",
             mfi_renal_replacement_therapy="renal replacement",
             seuil_transfu_10="high transfusion threshold",
             mfi_antiplatelets="platelet transfusion before I",
             ia_igs_2="SAPS2",
             csabad_hb="hemoglobin rate at I",
             csabad_eGFR="eGFR at I",
             csabad_lactate="lactate at I",
             gender="gender",
             ia_mac_cab="Mac cab score",
             initial_admission_unit="initial admission unit",
             ct_antiplatelets="chronic antiplatelets therapy",
             cm_coronary_artery_disease="chronic coronary disease",
             ncm_chronic_renal_disease="chronic renal disease",
             ncm_anemia="chronic anemia",
             mfi_rbc_transfusion="RBP transfusion before I ",
             mfi_coronary_revascularisation="PCI before I ",
             mfi_heparin="heparin treatment before I",
             ncm_chronic_disease="any chronic disease",
             ncm_active_recent_malignant_tumors="recent malignant tumor",
             ct_none_of_the_above="no medical treatment",
             ncm_none_of_the_above="no medical history",
             cm_chronic_heart_failure="chronic heart failure")

save(loveplot.out, file="DATA_PUBLIC/loveplot.out")
```

## Survival curves

Unadjusted HR

```{r,include=T,eval=FALSE}
bootstrap_number <- 100
#Estimate the unadjusted hazard ratio from a cox model
results_HR_unadjusted_cox <- c()
for (i in c(1:bootstrap_number)){
  DATA_input_KM <-   l_bootstrap_100[[i]]
  
  DATA_input_KM$T_obs_cox <- pmin(DATA_input_KM$T_obs,tau)
  DATA_input_KM$status_cox <- as.numeric( (DATA_input_KM$T_obs<tau &  DATA_input_KM$status == 1 ))
  fitS_outcome <- cph(Surv(T_obs_cox,status_cox)~ A,data=DATA_input_KM)
  coefHR <- fitS_outcome$coefficients["A=1"]
  unadjustedHR <- exp(coefHR)
  results_HR_unadjusted_cox <- c(results_HR_unadjusted_cox,unadjustedHR)
}


unadjusted_HR_mean <- mean(results_HR_unadjusted_cox)
unadjusted_HR_lower <- quantile(results_HR_unadjusted_cox,0.025)
unadjusted_HR_upper <- quantile(results_HR_unadjusted_cox,0.975)

result_HR <- list("unadjusted_HR_mean"=unadjusted_HR_mean,"unadjusted_HR_lower"=unadjusted_HR_lower,"unadjusted_HR_upper"=unadjusted_HR_upper)

save(result_HR, file="DATA_PUBLIC/result_HR_final")
```


Survival forest

```{r, include=T,eval=FALSE}
Y <- pmin(DATA$T_obs,tau)
Y.grid <- sort(unique(Y))

pool_survival_curves <- function(df){
  

  result_ATE <- estimate_ATE(df, tau, outcome_type="survival", Y.grid=Y.grid,
                             type_of_treatment_model="forest", type_of_outcome_model="forest", type_of_censoring_model="forest", 
                             method="AIPTW-AIPCW", 
                             outcome_name=X_outcome, censoring_name=X_censoring, treatment_name=X_confounding, 
                             estimate_individual=FALSE, outcome_learner="Slearner", censoring_learner="Slearner")

  resapply <- matrix(unlist(result_ATE[1:2]), ncol = 1)

  hazards <-apply(resapply, 2,function(listS1S0) {
      S1 <- listS1S0[1:length(Y.grid)]
      S0 <- listS1S0[(length(Y.grid)+1):(2*length(Y.grid))]
      return(estimate_average_hazard_ratio(S1,S0))
      })

  hazard <- mean(hazards)
  
  S1S0 <- rowMeans(resapply)
  
  S1 <- S1S0[1:length(Y.grid)]
  S0 <- S1S0[(length(Y.grid)+1):(2*length(Y.grid))]
  
  
  return(c("S1"=S1,"S0"=S0,"hazard"=hazard))
}

pooled_survival_curves <- pbsapply(l_bootstrap_100, pool_survival_curves)

write.csv(pooled_survival_curves,"DATA_PUBLIC/pooled_survival_curves_forest.csv", row.names = FALSE)

pooled_survival_curves_0.975 <- rowQuantiles(pooled_survival_curves,probs=0.975, na.rm=T)
pooled_survival_curves_0.025 <- rowQuantiles(pooled_survival_curves,probs=0.025, na.rm=T)


pooled_survival_curves_mean <- rowMeans(pooled_survival_curves, na.rm=T)
S_1 <-pooled_survival_curves_mean[1:length(Y.grid)]
S_0 <- pooled_survival_curves_mean[(length(Y.grid)+1):(2*length(Y.grid))]

S1_lower <-pooled_survival_curves_0.025[1:length(Y.grid)]
S0_lower <- pooled_survival_curves_0.025[(length(Y.grid)+1):(2*length(Y.grid))]

S1_upper <-pooled_survival_curves_0.975[1:length(Y.grid)]
S0_upper <- pooled_survival_curves_0.975[(length(Y.grid)+1):(2*length(Y.grid))]


AHR_mean <-pooled_survival_curves_mean[(2*length(Y.grid))+1]
AHR_lower <- pooled_survival_curves_0.025[(2*length(Y.grid))+1]
AHR_upper <- pooled_survival_curves_0.975[(2*length(Y.grid))+1]
```



```{r,include=T,eval=FALSE}
A_curve <- c(rep('1',length(Y.grid)),rep('0',length(Y.grid)))
strata_curve <- c(rep('A=1',length(Y.grid)),rep('A=0',length(Y.grid)))
S_curve <- c(S_1,S_0) 
Y_curve <- c(Y.grid,Y.grid)
out_wb1 <- data.frame(time = Y_curve, surv = S_curve, upper = NA, lower = NA, std.err = NA,strata= strata_curve,A= A_curve)
out_wb1$strata <- as.factor(out_wb1$strata)
out_wb1$A <- as.factor(out_wb1$A)
out_wb1$AHR_mean <- AHR_mean
out_wb1$AHR_lower <- AHR_lower
out_wb1$AHR_upper <- AHR_upper

write.csv(out_wb1,"DATA_PUBLIC/dataset_to_plot_adjusted_survival_curve_forest.csv", row.names = FALSE)
```



### Survival curve (figure)


```{r,include=FALSE,eval=T}
out_wb1 <- read.csv("DATA_PUBLIC/dataset_to_plot_adjusted_survival_curve_forest.csv")
load(file="DATA_PUBLIC/result_HR_final")

AHR_mean <- out_wb1$AHR_mean[1]
AHR_lower <- out_wb1$AHR_lower[1]
AHR_upper <- out_wb1$AHR_upper[1]

UHR_mean<-result_HR$unadjusted_HR_mean
UHR_lower<-result_HR$unadjusted_HR_lower
UHR_upper<-result_HR$unadjusted_HR_upper



## We build the curve here
adjusted_survival_curve <- ggsurvplot(out_wb1,
                    risk.table = F,
                    fun = function(y) y*100,
                     legend="bottom",
                     legend.title="",
                     legend.labs=c("No transfusion","Transfusion"),
                     ggtheme = theme_bw(),
                    palette = c("blue", "red"),
                    font.x=c(20,"bold", "black"),
                    xlab="Time (days)",
                    ylab="",
                    font.y=c(20,"bold", "black"),
                    font.tickslab = c(20,"bold", "black"),
                    font.legend = c(20,"bold", "black"),
                    font.legend.title = c(20,"bold", "black"))

adjusted_survival_curve <- adjusted_survival_curve + ggplot2::annotate("text",x = 200, y = 10,label = sprintf("Adjusted AHR: %s [%s,%s]", round(AHR_mean,2),round(AHR_lower,2),round(AHR_upper,2)),size=5)



DATA_input_KM <- DATA
DATA_input_KM$T_obs_cox <- pmin(DATA_input_KM$T_obs,tau)
DATA_input_KM$status_cox <- as.numeric( (DATA_input_KM$T_obs<tau &  DATA_input_KM$status == 1 ))
DATA_input_KM <- DATA_input_KM[,c("T_obs_cox", "status_cox", "A")]
KM_graphNM<-survfit( Surv(T_obs_cox,  status_cox) ~ A, data = DATA_input_KM)

save(KM_graphNM, DATA_input_KM, file="DATA_PUBLIC/unadjusted_KM_full")

Table<-ggsurvtable(KM_graphNM,data = DATA_input_KM,
                   color = "strata",
                   palette = c("blue", "red"),
                   y.text = FALSE,
                   xlim=c(0,365),
                   legend="none",
                   break.time.by = 91.25,ylab="") 


unadjusted_survival_curve <- ggsurvplot(KM_graphNM,
                    risk.table = F,
                    fun = function(y) y*100,
                    legend="bottom",
                    legend.title="",
                    legend.labs=c("No transfusion","Transfusion"),
                    ggtheme = theme_bw(),
                    palette = c("blue", "red"),
                    font.x=c(20,"bold", "black"),
                    xlab="Time (days)",
                    ylab="Survival probability (%)",
                    font.y=c(20,"bold", "black"),
                    font.tickslab = c(20,"bold", "black"),
                    font.legend = c(20,"bold", "black"),
                    font.legend.title = c(20,"bold", "black")
                    )

unadjusted_survival_curve[[1]]<- unadjusted_survival_curve[[1]] + ggplot2::annotate("text", x=200, y=10,label = sprintf("Unadjusted HR: %s [%s,%s]", round(UHR_mean,2),round(UHR_lower,2),round(UHR_upper,2)), size = 5)+ theme(legend.position = "none")


(unadjusted_survival_curve[[1]] + adjusted_survival_curve)  / guide_area()+plot_layout( guides = 'collect')
```

```{r,echo=FALSE, eval=T}
adjusted_survival_curve
unadjusted_survival_curve
```




# Session info for this script

```{r, echo = FALSE}
sessionInfo()
```

